|

### 2021-11-29 05-Chp-CPRD-Analysis.Rmd
Working version!

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
```
(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = TRUE}
When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
```
(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]

### 2021-11-29 08-Discussion.Rmd
Working version!

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
```

(ref:intro-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = FALSE}
Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
```

(ref:discussion-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]
